---
title: "Has transparency improved in clinical psychology? A repeated cross-sectional study (2012, 2018, 2024)"
format: html
execute:
  warning: false
  message: false
  echo: true
---

# Load packages

```{r}
library(tidyverse) # for general analysis and munging functions
library(here) # for accessing files
library(DescTools) # for confidence intervals
library(cowplot) # for multi-panel figures
library(knitr) # for tables
library(kableExtra) # for tables
library(readxl) # to load excel files
library(apa7) # for reporting p-values in apa format
```

# Load plot theme

A theme to be used for plots.

```{r}
theme_custom <- function () { 
  theme_grey(base_size = 20, base_family = "sans") %+replace% 
    theme(
      # plot margin
      plot.margin = unit(rep(0.5, 4), "cm"),
      # plot background and border
      plot.background = element_blank(),
      panel.background = element_blank(),
      panel.border = element_blank(),
      # grid lines
      panel.grid.major.x = element_blank(),
      panel.grid.major.y = element_line(linewidth = 0.5, linetype = 'dotted', color = "#cbcbcb"), 
      panel.grid.minor = element_blank(),
      # axis ticks and lines
      axis.ticks = element_blank(),
      axis.line = element_blank(),
      # legend
      legend.position = "bottom",
      legend.margin = margin(0),
      legend.background = element_blank(),
      legend.key = element_blank(),
      legend.title = element_text(size = 12, colour = "#333333"),
      legend.text.align = 0,
      legend.text = element_text(size = 20, colour = "#333333"),
      # faceting
      strip.background = element_rect(fill = "transparent", colour = NA),
      strip.text = element_text(size = 20, face = "bold", colour = "#333333", hjust = 0, margin = margin(b = 10, t = 10))
    )
}
```

# Load custom functions

```{r}
# Define a "not in" operator
`%notin%` <- Negate(`%in%`)

# This function will compute percentages and confidence intervals for specific variables and format them.

count_prop_ci <- function(data, ..., ci_method) {
  columns <- enquos(...)

  data <- data %>%
      count(!!!columns, .drop = FALSE) 
  
  data <- data %>%
      cbind(MultinomCI(data$n, conf.level = 0.95, sides = "two.sided", method=ci_method)) %>%
      mutate(N = sum(n)) %>%
    select(!!!columns, n, N, percent = est, ci_lwr = lwr.ci, ci_upr = upr.ci) %>%
    mutate(percent = percent*100, ci_lwr = ci_lwr*100, ci_upr = ci_upr*100, 
           report = paste0(n,' (',signif(percent,2),'% [',signif(ci_lwr,2),'%-',signif(ci_upr,2),'%])'))
  
  return(data)
}

# Same function as above but broken down by group (e.g., year)
count_prop_ci_by <- function(data, ..., group, ci_method) {
  cols <- enquos(...)
  grp  <- enquo(group)
  data %>%
    group_by(!!grp) %>%
    count(!!!cols, .drop = FALSE) %>%
    group_modify(~ {
      ci <- DescTools::MultinomCI(.x$n, conf.level = 0.95, sides = "two.sided", method = ci_method) %>%
        as_tibble()
      bind_cols(.x, ci) %>%
        mutate(
          N = sum(n),
          percent = est * 100,
          ci_lwr = lwr.ci * 100,
          ci_upr = upr.ci * 100,
          report = paste0(n, " (", signif(percent, 2), "% [", signif(ci_lwr, 2), "%–", signif(ci_upr, 2), "%])")
        )
    }) %>%
    ungroup() %>%
    select(!!grp, !!!cols, n, N, percent, ci_lwr, ci_upr, report)
}
```

# Load data

```{r}
# load the processed data which has coding differences resolved.
d <- read_excel(here('data','processed','coding_differences_resolved.xlsx'), col_types = 'text')
```

# Select consensus data only

```{r}
d_consensus <- d %>% filter(coder == "Consensus")
```

# Results

This section of code should reproduce the results reported in the manuscript.

## Article eligibility and characteristics

```{r}
# identify reasons articles were excluded
excluded_english <- d_consensus %>% filter(eligible_english == "NO") %>% nrow()
excluded_clinical <- d_consensus %>% filter(eligible_clinical == "NO") %>% nrow()
excluded_access <- d_consensus %>% filter(eligible_access == "NO") %>% nrow()
excluded_empirical <- d_consensus %>% filter(eligible_empirical == "NO") %>% nrow()
excluded_all <- sum(excluded_english, excluded_clinical, excluded_access, excluded_empirical)
```

```{r}
# select eligible data only
d_eligible <- d_consensus %>% filter(eligible_english == "YES", eligible_clinical == "YES", eligible_access == "YES", eligible_empirical == "YES")
```


We screened `r nrow(d_consensus)` randomly sampled articles and excluded `r excluded_all` (not English, n = `r excluded_english`; not clinical psychology, n = `r excluded_clinical`; not accessible, n = `r excluded_access`; not empirical, n = `r excluded_empirical`). This left `r nrow(d_eligible)` eligible articles (2012, n = `r d_eligible %>% filter(year == "2012") %>% nrow()`; 2018, n = `r d_eligible %>% filter(year == "2018") %>% nrow()`; 2024, n = `r d_eligible %>% filter(year == "2024") %>% nrow()`). This sample size was slightly less than our target of 200 eligible articles per year (N = 600) because a few articles included by one coder were excluded by the other (and vice versa).
  We classified the `r nrow(d_eligible)` eligible articles as primary research (n = `r d_eligible %>% filter(research_design == "Primary research study") %>% nrow()`), secondary research (n = `r d_eligible %>% filter(research_design == "Secondary analysis") %>% nrow()`), or both (n = `r d_eligible %>% filter(research_design == "Primary research study, Secondary analysis") %>% nrow()`). We classified data types as quantitative (n = `r d_eligible %>% filter(type_of_data == "Quantitative") %>% nrow()`), qualitative (n = `r d_eligible %>% filter(type_of_data == "Qualitative") %>% nrow()`), or both (n = `r d_eligible %>% filter(type_of_data == "Qualitative, Quantitative") %>% nrow()`). Subgroup analyses based on different research and data types are available in Supplementary Information X.

## Preregistration

```{r}
# Statements
prereg_statement_overall <- d_eligible %>%
  count_prop_ci(prereg_statement, ci_method = "sisonglaz")

prereg_statement_by_year <- d_eligible %>%
  count_prop_ci_by(prereg_statement, group = year, ci_method = "sisonglaz")

# Functional overall
prereg_functional_overall <- d_eligible %>%
  mutate(prereg_access_status = factor(prereg_access_status, levels = c("NO", "YES")), # show zero percentages too
         prereg_access_status = fct_na_value_to_level(prereg_access_status, level = "NO")) %>% # convert NAs to "NO"
  count_prop_ci(prereg_access_status, ci_method = "wilson")

# Functional by year
prereg_functional_by_year <- d_eligible %>%
  mutate(prereg_access_status = factor(prereg_access_status, levels = c("NO", "YES")), # show zero percentages too
         prereg_access_status = fct_na_value_to_level(prereg_access_status, level = "NO")) %>% # convert NAs to "NO"
  count_prop_ci_by(prereg_access_status, group = year, ci_method = "wilson")

# For Chi-Squared test 1
prereg_chi_1 <- prereg_functional_by_year %>% 
  filter(
    year %in% c("2012", "2018"), 
    prereg_access_status == "YES") %>% 
  select(year, case = n, N) %>% 
  mutate(noncase = N-case) %>% select(-N) %>% 
  pivot_longer(
    cols = c(case, noncase),
    names_to = "status",
    values_to = "count") %>%
    xtabs(count ~ year + status, data = .) %>% 
  chisq.test(correct = FALSE)

# For Chi-Squared test 2
prereg_chi_2 <- prereg_functional_by_year %>% 
  filter(
    year %in% c("2018", "2024"), 
    prereg_access_status == "YES") %>% 
  select(year, case = n, N) %>% 
  mutate(noncase = N-case) %>% select(-N) %>% 
  pivot_longer(
    cols = c(case, noncase),
    names_to = "status",
    values_to = "count") %>%
    xtabs(count ~ year + status, data = .) %>% 
  chisq.test(correct = FALSE)

# Reasons for non-functional
prereg_non_functional_reasons <- d_eligible %>%
  filter(prereg_access_status == "NO") %>%
  count(prereg_access_detail, .drop = FALSE)

# Access method
prereg_access_overall <- d_eligible %>%
  filter(prereg_statement == "YES — the statement says that there is a preregistration", prereg_access_status == "YES") %>%
  count(prereg_access_method, .drop = FALSE)
```

## Preregistration statements

`r prereg_statement_overall %>% filter(prereg_statement == "NO — there is no statement about preregistration") %>% pull(report)` articles did not contain a statement about preregistration, `r prereg_statement_overall %>% filter(prereg_statement == "YES — the statement says that there is no preregistration") %>% pull(report)` articles stated that there was no preregistration, and the remaining `r prereg_statement_overall %>% filter(prereg_statement == "YES — the statement says that there is a preregistration") %>% pull(report)` articles stated that there was a preregistration.

## Functional preregistration
Of the `r prereg_statement_overall %>% filter(prereg_statement == "YES — the statement says that there is a preregistration") %>% pull(n)` articles that stated there was a preregistration, we could not access the preregistration for `r d_eligible %>% count(prereg_statement, prereg_access_status) %>% filter(prereg_statement == "YES — the statement says that there is a preregistration", prereg_access_status == "NO") %>% pull(n)` articles, due to broken links (n = `r prereg_non_functional_reasons %>% filter(prereg_access_detail == "Broken link / ID") %>% pull(n)`) or unclear access instructions (n =  `r prereg_non_functional_reasons %>% filter(prereg_access_detail == "Unclear access instructions") %>% pull(n)`). Thus, the overall prevalence of functional preregistration was `r prereg_functional_overall %>% filter(prereg_access_status == "YES") %>% pull(report)` articles.

## Use of preregistration over time
The prevalence of functional preregistration increased over time (Figure 1). Specifically, we identified functional preregistrations for `r prereg_functional_by_year %>% filter(year == "2012", prereg_access_status == "YES") %>% pull(report)` articles in 2012, `r prereg_functional_by_year %>% filter(year == "2018", prereg_access_status == "YES") %>% pull(report)` articles in 2018, and `r prereg_functional_by_year %>% filter(year == "2024", prereg_access_status == "YES") %>% pull(report)` articles in 2024. Post-hoc (not preregistered) chi-square tests indicated that the increase in prevalence was not statistically significant between 2012 and 2018, χ²(`r unname(prereg_chi_1$parameter)`, N = `r sum(prereg_chi_1$observed)`) = `r unname(round(prereg_chi_1$statistic,2))`, `r apa_p(prereg_chi_1$p.value, inline = T)` and was statistically significant between 2018 and 2024, χ²(`r unname(prereg_chi_2$parameter)`, N = `r sum(prereg_chi_2$observed)`) = `r unname(round(prereg_chi_2$statistic,2))`, `r apa_p(prereg_chi_2$p.value, inline = T)`.
  
## Preregistration registries
The most commonly used registry for functional preregistration was `r prereg_access_overall %>% filter(n == max(n)) %>% pull(prereg_access_method)` (n = `r prereg_access_overall %>% filter(n == max(n)) %>% pull(n)` articles) with other platforms each accounting for less than `r prereg_access_overall %>% arrange(desc(n)) %>% slice(2) %>% mutate(n = n+1) %>% pull(n)` articles (for details, see Supplementary Table Z). No articles were `r #prereg_access_overall %>% filter(prereg_access_method == "Registered Report") %>% nrow()` Registered Reports.

# Measurement instruments

```{r}
# Statements
measures_statement_overall <- d_eligible %>%
  count_prop_ci(measures_statement, ci_method = "sisonglaz")

measures_statement_by_year <- d_eligible %>%
  count_prop_ci_by(measures_statement, group = year, ci_method = "sisonglaz")

# Reasons for not sharing

measures_reasons_overall <- d_eligible %>%
    mutate(measures_access_restrictions = factor(measures_access_restrictions, levels = c("NO", "YES"))) %>% # this makes sure zero percentages are shown
  count(measures_statement, measures_access_restrictions, .drop = FALSE)

# Functional
measures_functional_overall <- d_eligible %>%
  mutate(measures_access_status = factor(measures_access_status, levels = c("NO", "YES")), # show zero percentages too
         measures_access_status = fct_na_value_to_level(measures_access_status, level = "NO")) %>% # convert NAs to "NO"
  count_prop_ci(measures_access_status, ci_method = "wilson")

measures_functional_by_year <- d_eligible %>%
  mutate(measures_access_status = factor(measures_access_status, levels = c("NO", "YES")), # show zero percentages too
         measures_access_status = fct_na_value_to_level(measures_access_status, level = "NO")) %>% # convert NAs to "NO"
  count_prop_ci_by(measures_access_status, group = year, ci_method = "wilson")

# For Chi-Squared test 1
measures_chi_1 <- measures_functional_by_year %>% 
  filter(
    year %in% c("2012", "2018"), 
    measures_access_status == "YES") %>% 
  select(year, case = n, N) %>% 
  mutate(noncase = N-case) %>% select(-N) %>% 
  pivot_longer(
    cols = c(case, noncase),
    names_to = "status",
    values_to = "count") %>%
    xtabs(count ~ year + status, data = .) %>% 
  chisq.test(correct = FALSE)

# For Chi-Squared test 2
measures_chi_2 <- measures_functional_by_year %>% 
  filter(
    year %in% c("2018", "2024"), 
    measures_access_status == "YES") %>% 
  select(year, case = n, N) %>% 
  mutate(noncase = N-case) %>% select(-N) %>% 
  pivot_longer(
    cols = c(case, noncase),
    names_to = "status",
    values_to = "count") %>%
    xtabs(count ~ year + status, data = .) %>% 
  chisq.test(correct = FALSE)

# Reasons for non-functional
measures_non_functional_reasons <- d_eligible %>%
  filter(measures_access_status == "NO") %>%
  count(measures_access_detail, .drop = FALSE)

# Access method
measures_access_method_overall <- d_eligible %>%
  filter(measures_statement %in% c("YES — no explicit statement but measures found", "YES — the statement says that all or some measures are available"), measures_access_status == "YES") %>%
  count(measures_access_method, .drop = FALSE)

```

The vast majority of articles did not share any measurement instruments; however, the prevalence of measurement instrument sharing has increased modestly over time. 

## Availability statements for measurement instruments
`r measures_statement_overall %>% filter(measures_statement == "NO — there is no measures availability statement") %>% pull(report)` articles did not contain any statements about the availability of primary measurement instruments; `r measures_statement_overall %>% filter(measures_statement == "UNCLEAR — the statement says that the measures are available on request") %>% pull(report)` articles stated that measurement instruments were only available on request; and `r measures_statement_overall %>% filter(measures_statement == "YES — the statement says that the measures are not available") %>% pull(report)` article explicitly said that measurement instruments were not available. Of the remaining articles, `r measures_statement_overall %>% filter(measures_statement == "YES — the statement says that all or some measures are available") %>% pull(report)` stated that at least one measurement instrument was available and for an additional `r measures_statement_overall %>% filter(measures_statement == "YES — no explicit statement but measures found") %>% pull(report)` we incidentally found a measurement instrument even though the article had no statements about measurement instrument availability.

## Functional availability of measurement instruments
Of the `r measures_statement_overall %>% filter(measures_statement == "YES — the statement says that all or some measures are available") %>% pull(n)` articles which stated that at least one primary measurement instrument was available, we could not access the instrument in `r d_eligible %>% count(measures_statement, measures_access_status) %>% filter(measures_statement == "YES — the statement says that all or some measures are available", measures_access_status == "NO") %>% pull(n)` cases, because we could not find any measurement instrument at the provided link (n = `r measures_non_functional_reasons %>% filter(measures_access_detail == "Cannot find measures") %>% pull(n)`), a fee was required (n = `r measures_non_functional_reasons %>% filter(measures_access_detail == "Fee required") %>% pull(n)`), or a link was broken (n = `r measures_non_functional_reasons %>% filter(measures_access_detail == "Broken link") %>% pull(n)`). Thus, the overall prevalence of articles functionally sharing at least one measurement instrument (including the `r measures_statement_overall %>% filter(measures_statement == "YES — no explicit statement but measures found") %>% pull(n)` articles where we incidentally found a measurement instrument) was `r measures_functional_overall %>% filter(measures_access_status == "YES") %>% pull(report)` articles. 

## Availability of measurement instruments over time
Functional sharing of primary measurement instruments has increased over time (Figure 1). Specifically, we found functional sharing of at least one primary measurement instrument for `r measures_functional_by_year %>% filter(year == "2012", measures_access_status == "YES") %>% pull(report)` articles in 2012, `r measures_functional_by_year %>% filter(year == "2018", measures_access_status == "YES") %>% pull(report)` articles in 2018, and `r measures_functional_by_year %>% filter(year == "2024", measures_access_status == "YES") %>% pull(report)` articles in 2024. Post-hoc (not preregistered) chi-square tests indicated a statistically significant increase in the functional sharing of measurement instruments between 2012 and 2018, χ²(`r unname(measures_chi_1$parameter)`, N = `r sum(measures_chi_1$observed)`) = `r unname(round(measures_chi_1$statistic,2))`, `r apa_p(measures_chi_1$p.value, inline = T)`, and no significant increase between 2012 and 2018, χ²(`r unname(measures_chi_2$parameter)`, N = `r sum(measures_chi_2$observed)`) = `r unname(round(measures_chi_2$statistic,2))`, `r apa_p(measures_chi_2$p.value, inline = T)`.

## Justifications for restricting access to measurement instruments
Of the `r d_eligible %>% filter(measures_statement %in% c("YES — the statement says that the measures are not available", "UNCLEAR — the statement says that the measures are available on request")) %>% nrow()` articles that restricted access (i.e., said measurement instruments were only available on request or explicitly stated that measurement instruments were not available) `r measures_reasons_overall %>% filter(measures_statement %in% c("YES — the statement says that the measures are not available", "UNCLEAR — the statement says that the measures are available on request"), measures_access_restrictions == "YES") %>% pull(n) %>% sum()` provided a reason for limiting access.

## Methods of sharing measurement instruments
The most common functional sharing method was `r measures_access_method_overall %>% filter(n == max(n)) %>% pull(measures_access_method)` (n = `r measures_access_method_overall %>% filter(n == max(n)) %>% pull(n)` articles) followed by `r measures_access_method_overall %>% arrange(desc(n)) %>% slice(2) %>% pull(measures_access_method)` (n = `r measures_access_method_overall %>% arrange(desc(n)) %>% slice(2) %>% pull(n)` articles). Other sharing methods each accounted for less than `r measures_access_method_overall %>% arrange(desc(n)) %>% slice(3) %>% mutate(n = n+1) %>% pull(n)` articles (for details, see Supplementary Table Z). 

# Data

```{r}
# Statements
data_statement_overall <- d_eligible %>%
  count_prop_ci(data_statement, ci_method = "sisonglaz")

data_statement_by_year <- d_eligible %>%
  count_prop_ci_by(data_statement, group = year, ci_method = "sisonglaz")

# Reasons for not sharing
data_reasons_overall <- d_eligible %>%
  count(data_statement, data_access_restrictions)

data_reasons_type <- d_eligible %>% 
  filter(data_statement %in% c("UNCLEAR — the statement says that the data are available on request", "YES — the statement says that the data are not available"), data_access_restrictions == "YES") %>% 
  count(data_access_restrictions_type) %>% 
  arrange(desc(n))

# Functional
data_functional_overall <- d_eligible %>%
  mutate(data_access_status = factor(data_access_status, levels = c("NO", "YES")), # show zero percentages too
         data_access_status = fct_na_value_to_level(data_access_status, level = "NO")) %>% # convert NAs to "NO"
  count_prop_ci(data_access_status, ci_method = "wilson")

data_functional_by_year <- d_eligible %>%
  mutate(data_access_status = factor(data_access_status, levels = c("NO", "YES")), # show zero percentages too
         data_access_status = fct_na_value_to_level(data_access_status, level = "NO")) %>% # convert NAs to "NO"
  count_prop_ci_by(data_access_status, group = year, ci_method = "wilson")

# For Chi-Squared test 1
data_chi_1 <- data_functional_by_year %>% 
  filter(
    year %in% c("2012", "2018"), 
    data_access_status == "YES") %>% 
  select(year, case = n, N) %>% 
  mutate(noncase = N-case) %>% select(-N) %>% 
  pivot_longer(
    cols = c(case, noncase),
    names_to = "status",
    values_to = "count") %>%
    xtabs(count ~ year + status, data = .) %>% 
  chisq.test(correct = FALSE)

# For Chi-Squared test 2
data_chi_2 <- data_functional_by_year %>% 
  filter(
    year %in% c("2018", "2024"), 
    data_access_status == "YES") %>% 
  select(year, case = n, N) %>% 
  mutate(noncase = N-case) %>% select(-N) %>% 
  pivot_longer(
    cols = c(case, noncase),
    names_to = "status",
    values_to = "count") %>%
    xtabs(count ~ year + status, data = .) %>% 
  chisq.test(correct = FALSE)

# Reasons for non-functional
data_non_functional_reasons <- d_eligible %>%
  filter(data_statement == "YES — the statement says that the data are available", data_access_status == "NO") %>%
  count(data_access_detail, .drop = FALSE)

# Access method
data_access_method_overall <- d_eligible %>%
  filter(data_statement == "YES — the statement says that the data are available", data_access_status == "YES") %>%
  count(data_access_method, .drop = FALSE)
```

The vast majority of articles did not share any raw or primary level data; however, the prevalence of data sharing has increased modestly over time. 

## Availability statements for data

`r data_statement_overall %>% filter(data_statement == "NO — there is no data availability statement") %>% pull(report)` articles did not contain any statement about data availability; `r data_statement_overall %>% filter(data_statement == "UNCLEAR — the statement says that the data are available on request") %>% pull(report)` articles stated that the data were only available on request; `r data_statement_overall %>% filter(data_statement == "YES — the statement says that the data are not available") %>% pull(report)` articles explicitly stated that the data were not available; and the remaining `r data_statement_overall %>% filter(data_statement == "YES — the statement says that the data are available") %>% pull(report)` articles stated that the data were available.

## Functional availability of data
Of the `r data_statement_overall %>% filter(data_statement == "YES — the statement says that the data are available") %>% pull(n)` articles that said data were available, we could not access the data in `r d_eligible %>% count(data_statement, data_access_status) %>% filter(data_statement == "YES — the statement says that the data are available", data_access_status == "NO") %>% pull(n)` cases, because we could not find any data at the provided link (n = `r data_non_functional_reasons %>% filter(data_access_detail == "Cannot find data") %>% pull(n)`), unclear access instructions (n = `r data_non_functional_reasons %>% filter(data_access_detail == "Unclear access instructions") %>% pull(n)`), a link was broken (n = `r data_non_functional_reasons %>% filter(data_access_detail == "Broken link") %>% pull(n)`), or access was restricted (n = `r data_non_functional_reasons %>% filter(data_access_detail == "Access restricted") %>% pull(n)`). Thus, the overall prevalence of articles functionally sharing raw/primary data was `r data_functional_overall %>% filter(data_access_status == "YES") %>% pull(report)` articles. 

## Availability of data over time
There has been a modest increase in functional sharing of raw/primary data over time (Figure 1). Specifically, we found functional data sharing for `r data_functional_by_year %>% filter(year == "2012", data_access_status == "YES") %>% pull(report)` articles in 2012, `r data_functional_by_year %>% filter(year == "2018", data_access_status == "YES") %>% pull(report)` articles in 2018, and `r data_functional_by_year %>% filter(year == "2024", data_access_status == "YES") %>% pull(report)` articles in 2024. Post-hoc (not preregistered) chi-square tests indicated a no statistically significant increase in functional data sharing between 2012 and 2018, χ²(`r unname(data_chi_1$parameter)`, N = `r sum(data_chi_1$observed)`) = `r round(unname(data_chi_1$statistic),2)`, `r apa_p(data_chi_1$p.value, inline = T)` and a significant increase between 2018 and 2024, χ²(`r unname(data_chi_2$parameter)`, N = `r sum(data_chi_2$observed)`) = `r round(unname(data_chi_2$statistic),2)`, `r apa_p(data_chi_2$p.value, inline = T)`.

## Justifications for restricting access to data
Of the `r d_eligible %>% filter(data_statement %in% c("UNCLEAR — the statement says that the data are available on request", "YES — the statement says that the data are not available")) %>% nrow()` articles that restricted data access (i.e., said data were only available on request or explicitly stated that data were not available), `r d_eligible %>% filter(data_statement %in% c("UNCLEAR — the statement says that the data are available on request", "YES — the statement says that the data are not available")) %>% filter(data_access_restrictions == "NO") %>% nrow()` did not provide a justification. Of the `r d_eligible %>% filter(data_statement %in% c("UNCLEAR — the statement says that the data are available on request", "YES — the statement says that the data are not available")) %>% filter(data_access_restrictions == "YES") %>% nrow()` articles that did provide a justification for restricting access, the justifications were participant privacy/confidentiality (n = `r data_reasons_type %>% filter(data_access_restrictions_type == "Privacy/confidentiality") %>% pull(n)`), participants were not asked to consent to data sharing (n = `r data_reasons_type %>% filter(data_access_restrictions_type == "No consent") %>% pull(n)`), an ethics board did not permit data sharing (n = `r data_reasons_type %>% filter(data_access_restrictions_type == "Ethics board") %>% pull(n)`), a study sponsor did not permit data sharing (n = `r data_reasons_type %>% filter(data_access_restrictions_type == "Study sponsor") %>% pull(n)`), a data use agreement did not permit data sharing (n = `r data_reasons_type %>% filter(data_access_restrictions_type == "data use agreement") %>% pull(n)`), and the authors did not have permission to share (from an unspecified authority; n = `r data_reasons_type %>% filter(data_access_restrictions_type == "No permission (unclear from who)") %>% pull(n)`).

## Methods of sharing data
The most common functional sharing method was `r data_access_method_overall %>% filter(n == max(n)) %>% pull(data_access_method)` (n = `r data_access_method_overall %>% filter(n == max(n)) %>% pull(n)` articles). Other sharing methods each accounted for less than `r data_access_method_overall %>% arrange(desc(n)) %>% slice(2) %>% mutate(n = n+1) %>% pull(n)` articles (for details, see Supplementary Table Z). 

# Analysis scripts

```{r}
# Statements
analysis_statement_overall <- d_eligible %>%
  count_prop_ci(analysis_statement, ci_method = "sisonglaz")

analysis_statement_by_year <- d_eligible %>%
  count_prop_ci_by(analysis_statement, group = year, ci_method = "sisonglaz")

# Reasons for not sharing
analysis_reasons_overall <- d_eligible %>%
  count(analysis_statement, analysis_access_restrictions)

# Functional 
analysis_functional_overall <- d_eligible %>%
  mutate(analysis_access_status = factor(analysis_access_status, levels = c("NO", "YES")), # show zero percentages too
         analysis_access_status = fct_na_value_to_level(analysis_access_status, level = "NO")) %>% # convert NAs to "NO"
  count_prop_ci(analysis_access_status, ci_method = "wilson")

analysis_functional_by_year <- d_eligible %>%
  mutate(analysis_access_status = factor(analysis_access_status, levels = c("NO", "YES")), # show zero percentages too
         analysis_access_status = fct_na_value_to_level(analysis_access_status, level = "NO")) %>% # convert NAs to "NO"
  count_prop_ci_by(analysis_access_status, group = year, ci_method = "wilson")

# For Chi-Squared test
analysis_chi <- analysis_functional_by_year %>% 
  filter(
    year %in% c("2012", "2024"), 
    analysis_access_status == "YES") %>% 
  select(year, case = n, N) %>% 
  mutate(noncase = N-case) %>% select(-N) %>% 
  pivot_longer(
    cols = c(case, noncase),
    names_to = "status",
    values_to = "count") %>%
    xtabs(count ~ year + status, data = .) %>% 
  chisq.test(correct = FALSE)

# Reasons for non-functional
analysis_non_functional_reasons <- d_eligible %>%
  filter(analysis_access_status == "NO") %>%
  count(analysis_access_detail, .drop = FALSE)

# Access method
analysis_access_method_overall <- d_eligible %>%
  filter(analysis_statement %in% c("YES — no explicit statement but analysis scripts found", "YES — the statement says that the analysis scripts are available"), analysis_access_status == "YES") %>%
  count(analysis_access_method, .drop = FALSE)

```
The vast majority of articles did not share analysis scripts; however, the prevalence of analysis scripts has increased modestly over time.

## Availability statements for analysis scripts
`r analysis_statement_overall %>% filter(analysis_statement == "NO — there is no analysis script availability statement") %>% pull(report)` articles did not contain any statement about analysis script availability; `r analysis_statement_overall %>% filter(analysis_statement == "UNCLEAR — the statement says that the analysis scripts are available on request") %>% pull(report)` articles stated that the analysis scripts were only available on request; and `r analysis_statement_overall %>% filter(analysis_statement == "YES — the statement says that the analysis scripts are not available") %>% pull(report)` articles explicitly stated that the analysis scripts were not available. Of the remaining articles, `r analysis_statement_overall %>% filter(analysis_statement == "YES — the statement says that the analysis scripts are available") %>% pull(report)` stated that the analysis scripts were available and for an additional `r analysis_statement_overall %>% filter(analysis_statement == "YES — no explicit statement but analysis scripts found") %>% pull(report)` we incidentally found analysis scripts even though the article had no statements about analysis script availability.

## Functional availability of analysis scripts
Of the `r analysis_statement_overall %>% filter(analysis_statement == "YES — the statement says that the analysis scripts are available") %>% pull(n)` articles that said analysis scripts were available, we could not access the analysis scripts in `r d_eligible %>% count(analysis_statement, analysis_access_status) %>% filter(analysis_statement == "YES — the statement says that the analysis scripts are available", analysis_access_status == "NO") %>% pull(n)` cases, because we could not find any analysis scripts at the provided link (n = `r analysis_non_functional_reasons %>% filter(analysis_access_detail == "Cannot find analysis scripts") %>% pull(n)`) or the access instructions were unclear (n = `r analysis_non_functional_reasons %>% filter(analysis_access_detail == "Unclear access instructions") %>% pull(n)`). Thus, the overall prevalence of articles functionally sharing analysis scripts (including the `r analysis_statement_overall %>% filter(analysis_statement == "YES — no explicit statement but analysis scripts found") %>% pull(n)` articles where we incidentally found the analysis scripts) was `r analysis_functional_overall %>% filter(analysis_access_status == "YES") %>% pull(report)` articles. 

## Availability of analysis scripts over time
There has been a modest increase in functional sharing of analysis scripts over time (Figure 1). Specifically, we found functional sharing of analysis scripts for `r analysis_functional_by_year %>% filter(year == "2012", analysis_access_status == "YES") %>% pull(report)` articles in 2012, `r analysis_functional_by_year %>% filter(year == "2018", analysis_access_status == "YES") %>% pull(report)` articles in 2018, and `r analysis_functional_by_year %>% filter(year == "2024", analysis_access_status == "YES") %>% pull(report)` articles in 2024. A post-hoc (not preregistered) chi-square test indicated a statistically significant increase in the functional sharing of analysis scripts between 2012 and 2024, χ²(`r unname(analysis_chi$parameter)`, N = `r sum(analysis_chi$observed)`) = `r round(unname(analysis_chi$statistic),2)`, `r apa_p(analysis_chi$p.value, inline = T)`.

## Justifications for restricting access to analysis scripts
Of the `r d_eligible %>% filter(analysis_statement %in% c("UNCLEAR — the statement says that the analysis scripts are available on request", "YES — the statement says that the analysis scripts are not available")) %>% nrow()` articles that restricted access to analysis scripts (i.e., said analysis scripts were only available on request or explicitly stated that analysis scripts were not available), `r d_eligible %>% filter(analysis_statement %in% c("UNCLEAR — the statement says that the analysis scripts are available on request", "YES — the statement says that the analysis scripts are not available")) %>% filter(analysis_access_restrictions == "YES") %>% nrow()` provided a justification. 

## Methods of sharing analysis scripts
The most common functional sharing method was `r analysis_access_method_overall %>% filter(n == max(n)) %>% pull(analysis_access_method)` (n = `r analysis_access_method_overall %>% filter(n == max(n)) %>% pull(n)` articles). Other sharing methods each accounted for less than `r analysis_access_method_overall %>% arrange(desc(n)) %>% slice(2) %>% mutate(n = n+1) %>% pull(n)` articles (for details, see Supplementary Table Z). 

# Data and analysis scripts
```{r}
# Functional 
data_and_analysis_functional_overall <- d_eligible %>%
  mutate( 
    analysis_access_status = factor(analysis_access_status, levels = c("NO", "YES")), # show zero percentages too
    data_access_status = factor(data_access_status, levels = c("NO", "YES")), # show zero percentages too
    analysis_access_status = fct_na_value_to_level(analysis_access_status, level = "NO"), # convert NAs to "NO"
    data_access_status = fct_na_value_to_level(data_access_status, level = "NO")) %>% # convert NAs to "NO"
  count_prop_ci(data_access_status, analysis_access_status, ci_method = "wilson")

data_and_analysis_functional_by_year <- d_eligible %>%
  mutate( 
    analysis_access_status = factor(analysis_access_status, levels = c("NO", "YES")), # show zero percentages too
    data_access_status = factor(data_access_status, levels = c("NO", "YES")), # show zero percentages too
    analysis_access_status = fct_na_value_to_level(analysis_access_status, level = "NO"), # convert NAs to "NO"
    data_access_status = fct_na_value_to_level(data_access_status, level = "NO")) %>% # convert NAs to "NO"
  count_prop_ci_by(data_access_status, analysis_access_status, group = year, ci_method = "wilson")

# For Chi-Squared test
data_and_analysis_chi <- data_and_analysis_functional_by_year %>% 
  filter(
    year %in% c("2012", "2024"), 
    data_access_status == "YES",
    analysis_access_status == "YES") %>% 
  select(year, case = n, N) %>% 
  mutate(noncase = N-case) %>% select(-N) %>% 
  pivot_longer(
    cols = c(case, noncase),
    names_to = "status",
    values_to = "count") %>%
    xtabs(count ~ year + status, data = .) %>% 
  chisq.test(correct = FALSE)
```

To gauge the potential computational reproducibility of articles, we also estimated the prevalence of articles that shared both raw/primary data *and* analysis scripts. Sharing of both data and analysis scripts increased from `r data_and_analysis_functional_by_year %>% filter(year == "2012", data_access_status == "YES", analysis_access_status == "YES") %>% pull(report)` articles in 2012, to `r data_and_analysis_functional_by_year %>% filter(year == "2018", data_access_status == "YES", analysis_access_status == "YES") %>% pull(report)` article in 2018, and `r data_and_analysis_functional_by_year %>% filter(year == "2024", data_access_status == "YES", analysis_access_status == "YES") %>% pull(report)` articles in 2024. A post-hoc (not preregistered) chi-square test indicated a statistically significant increase in the proportion of articles sharing both data and analysis scripts between 2012 and 2024, χ²(`r unname(data_and_analysis_chi$parameter)`, N = `r sum(data_and_analysis_chi$observed)`) = `r round(unname(data_and_analysis_chi$statistic),2)`, `r apa_p(data_and_analysis_chi$p.value, inline = T)`.

# Reporting guidelines

```{r}
# Statements
reporting_statement_overall <- d_eligible %>%
  count_prop_ci(reporting_statement, ci_method = "sisonglaz")

reporting_statement_by_year <- d_eligible %>%
  count_prop_ci_by(reporting_statement, group = year, ci_method = "sisonglaz")

# For Chi-Squared test
reporting_chi <- reporting_statement_by_year %>% 
  filter(
    year %in% c("2012", "2024"), 
    reporting_statement == "YES — the statement discloses use of at least one reporting guideline") %>% 
  select(year, case = n, N) %>% 
  mutate(noncase = N-case) %>% select(-N) %>% 
  pivot_longer(
    cols = c(case, noncase),
    names_to = "status",
    values_to = "count") %>%
    xtabs(count ~ year + status, data = .) %>% 
  chisq.test(correct = FALSE)

# Guideline type
reporting_type_overall <- d_eligible %>%
  filter(reporting_statement == "YES — the statement discloses use of at least one reporting guideline") %>%
  count(reporting_type)
```
## Use of reporting guidelines
The vast majority of articles did not use reporting guidelines; however, the use of reporting guidelines has increased modestly over time. Specifically, `r reporting_statement_overall %>% filter(reporting_statement == "NO — there is no statement related to reporting guidelines") %>% pull(report)` articles did not refer to a reporting guideline and the remaining `r reporting_statement_overall %>% filter(reporting_statement == "YES — the statement discloses use of at least one reporting guideline") %>% pull(report)` articles did refer to a reporting guideline. 

## Use of reporting guidelines over time
There has been a modest increase in the use of reporting guidelines over time (Figure 1). Specifically, we found use of reporting guidelines in `r reporting_statement_by_year %>% filter(year == "2012", reporting_statement == "YES — the statement discloses use of at least one reporting guideline") %>% pull(report)` article in 2012, `r reporting_statement_by_year %>% filter(year == "2018", reporting_statement == "YES — the statement discloses use of at least one reporting guideline") %>% pull(report)` articles in 2018, and `r reporting_statement_by_year %>% filter(year == "2024", reporting_statement == "YES — the statement discloses use of at least one reporting guideline") %>% pull(report)` articles in 2024. A post-hoc (not preregistered) chi-square test indicated a statistically significant increase in the use of reporting guidelines between 2012 and 2024, χ²(`r unname(reporting_chi$parameter)`, N = `r sum(reporting_chi$observed)`) = `r round(unname(reporting_chi$statistic),2)`, `r apa_p(reporting_chi$p.value, inline = T)`.

## Types of reporting guidelines
The most commonly used reporting guideline was `r reporting_type_overall %>% filter(n == max(n)) %>% pull(reporting_type)` (n = `r reporting_type_overall %>% filter(n == max(n)) %>% pull(n)` articles). Other reporting guidelines each accounted for less than `r reporting_type_overall %>% arrange(desc(n)) %>% slice(2) %>% mutate(n = n+1) %>% pull(n)` articles (for details, see Supplementary Table Z). 

# Funding disclosures

```{r}
# Statements
funding_statement_overall <- d_eligible %>%
  mutate(funding_statement = case_when(
    funding_statement %in% c("YES — the statement discloses at least one source of funding","YES — the statement says that there was no relevant funding") ~ "Yes", 
    funding_statement == "NO — there is no funding statement" ~ "No")) %>%
  count_prop_ci(funding_statement, ci_method = "wilson")

funding_statement_by_year <- d_eligible %>%
  mutate(funding_statement = case_when(
    funding_statement %in% c("YES — the statement discloses at least one source of funding","YES — the statement says that there was no relevant funding") ~ "Yes", 
    funding_statement == "NO — there is no funding statement" ~ "No")) %>%
  count_prop_ci_by(funding_statement, group = year, ci_method = "wilson")

# For Chi-Squared test
funding_chi <- funding_statement_by_year %>% 
  filter(
    year %in% c("2012", "2024"), 
    funding_statement == "Yes") %>% 
  select(year, case = n, N) %>% 
  mutate(noncase = N-case) %>% select(-N) %>% 
  pivot_longer(
    cols = c(case, noncase),
    names_to = "status",
    values_to = "count") %>%
    xtabs(count ~ year + status, data = .) %>% 
  chisq.test(correct = FALSE)

# Statement type
funding_detail_overall <- d_eligible %>%
  count_prop_ci(funding_statement, ci_method = "sisonglaz")
```
## Funding statements
`r funding_statement_overall %>% filter(funding_statement == "Yes") %>% pull(report)` articles contained a funding statement and the remaining `r funding_statement_overall %>% filter(funding_statement == "No") %>% pull(report)` articles did not. Of the `r funding_statement_overall %>% filter(funding_statement == "Yes") %>% pull(n)` articles that contained a funding statement, `r funding_detail_overall %>% filter(funding_statement == "YES — the statement discloses at least one source of funding") %>% pull(n)` disclosed at least one source of funding and `r funding_detail_overall %>% filter(funding_statement == "YES — the statement says that there was no relevant funding") %>% pull(n)` explicitly stated that there was no relevant funding.

## Funding statements over time
We did not find evidence for increased use of funding statements over time (Figure 1). Specifically, we found funding statements in `r funding_statement_by_year %>% filter(year == "2012", funding_statement == "Yes") %>% pull(report)` articles in 2012, `r funding_statement_by_year %>% filter(year == "2018", funding_statement == "Yes") %>% pull(report)` articles in 2018, and `r funding_statement_by_year %>% filter(year == "2024", funding_statement == "Yes") %>% pull(report)` articles in 2024. A post-hoc (not preregistered) chi-square test indicated no statistically significant change in the use of funding statements between 2012 and 2024, χ²(`r unname(funding_chi$parameter)`, N = `r sum(funding_chi$observed)`) = `r round(unname(funding_chi$statistic),2)`, `r apa_p(funding_chi$p.value, inline = T)`.

# Conflict of interest disclosures

```{r}
# Statements
coi_statement_overall <- d_eligible %>%
  mutate(coi_statement = case_when(
    coi_statement %in% c("YES — the statement discloses at least one conflict of interest","YES — the statement says that there were no conflicts of interest") ~ "Yes", 
    coi_statement == "NO — there is no conflict of interest statement" ~ "No")) %>%
  count_prop_ci(coi_statement, ci_method = "wilson")

coi_statement_by_year <- d_eligible %>%
  mutate(coi_statement = case_when(
    coi_statement %in% c("YES — the statement discloses at least one conflict of interest","YES — the statement says that there were no conflicts of interest") ~ "Yes", 
    coi_statement == "NO — there is no conflict of interest statement" ~ "No")) %>%
  count_prop_ci_by(coi_statement, group = year, ci_method = "wilson")

# Chi-Squared test 2012 vs 2024
coi_chi_1 <- coi_statement_by_year %>% 
  filter(
    year %in% c("2012", "2024"), 
    coi_statement == "Yes") %>% 
  select(year, case = n, N) %>% 
  mutate(noncase = N-case) %>% select(-N) %>% 
  pivot_longer(
    cols = c(case, noncase),
    names_to = "status",
    values_to = "count") %>%
    xtabs(count ~ year + status, data = .) %>% 
  chisq.test(correct = FALSE)

# Statement type
coi_detail_overall <- d_eligible %>%
  count_prop_ci(coi_statement, ci_method = "sisonglaz")
```
## Conflict of interest statements
`r coi_statement_overall %>% filter(coi_statement == "Yes") %>% pull(report)` articles contained a conflict of interest statement and the remaining `r coi_statement_overall %>% filter(coi_statement == "No") %>% pull(report)` articles did not. Of the `r coi_statement_overall %>% filter(coi_statement == "Yes") %>% pull(n)` articles that contained a conflict of interest statement, `r coi_detail_overall %>% filter(coi_statement == "YES — the statement discloses at least one conflict of interest") %>% pull(n)` disclosed at least one conflict of interest and `r coi_detail_overall %>% filter(coi_statement == "YES — the statement says that there were no conflicts of interest") %>% pull(n)` explicitly stated that there were no conflicts of interest.

## Conflict of interest statements over time
There has been a substantial increase in the use of conflict of interest statements over time (Figure 1). Specifically, we found conflict of interest statements in `r coi_statement_by_year %>% filter(year == "2012", coi_statement == "Yes") %>% pull(report)` articles in 2012, `r coi_statement_by_year %>% filter(year == "2018", coi_statement == "Yes") %>% pull(report)` articles in 2018, and `r coi_statement_by_year %>% filter(year == "2024", coi_statement == "Yes") %>% pull(report)` articles in 2024. A post-hoc (not preregistered) chi-square test indicated a statistically significant increase in the use of conflict of interest statements between 2012 and 2024, χ²(`r unname(coi_chi_1$parameter)`, N = `r sum(coi_chi_1$observed)`) = `r round(unname(coi_chi_1$statistic),2)`, `r apa_p(coi_chi_1$p.value, inline = T)`.

# Plots

```{r}
 plot_data <- bind_rows(

  prereg_functional_by_year %>%
    filter(prereg_access_status == "YES") %>%
    mutate(practice = "Preregistration", var = "prereg_functional", type = "functional") %>%
    select(year, practice, var, type, n, N, percent, ci_lwr, ci_upr),

  measures_functional_by_year %>%
    filter(measures_access_status == "YES") %>%
    mutate(practice = "Measurement instruments", var = "measures_functional", type = "functional") %>%
    select(year, practice, var, type, n, N, percent, ci_lwr, ci_upr),

  data_functional_by_year %>%
    filter(data_access_status == "YES") %>%
    mutate(practice = "Data", var = "data_functional", type = "functional") %>%
    select(year, practice, var, type, n, N, percent, ci_lwr, ci_upr),

  analysis_functional_by_year %>%
    filter(analysis_access_status == "YES") %>%
    mutate(practice = "Analysis scripts",var = "analysis_functional", type = "functional") %>%
    select(year, practice, var, type, n, N, percent, ci_lwr, ci_upr),

  reporting_statement_by_year %>%
    filter(reporting_statement == "YES — the statement discloses use of at least one reporting guideline") %>%
    mutate(practice = "Reporting guidelines",var = "reporting_any", type = "statement") %>%
    select(year, practice, var, type, n, N, percent, ci_lwr, ci_upr),
  
  funding_statement_by_year %>%
    filter(funding_statement == "Yes") %>%
    mutate(practice = "Funding",var = "funding_statement_any", type = "statement") %>%
    select(year, practice, var, type, n, N, percent, ci_lwr, ci_upr),

  coi_statement_by_year %>%
    filter(coi_statement == "Yes") %>%
    mutate(practice = "Conflict of interest",var = "coi_statement_any", type = "statement") %>%
    select(year, practice, var, type, n, N, percent, ci_lwr, ci_upr)
)
```

```{r core_practices_plot, fig.path = "figs/", fig.width = 10/2.54, fig.height = 8/2.54}
plot_core <- plot_data %>%
  filter(practice %in% c("Preregistration","Measurement instruments","Data","Analysis scripts"),
         type == "functional") %>%
  mutate(practice = factor(practice, levels = c("Preregistration","Measurement instruments","Data","Analysis scripts")),
         type = factor(type),
         type = fct_recode(type, "Functionally available" = "functional")) %>%
  ggplot(aes(x = year, y = percent)) +
  facet_wrap(. ~ practice) +
    geom_pointrange(position = position_dodge(width = .2), shape = 21, size = 1, colour = "#333333",
      aes(
        fill = type,
        ymin = ci_lwr,
        ymax = ci_upr),
      show.legend = FALSE) +
    geom_text(
             aes(label = paste0(signif(percent,2),'%')),
             show.legend = FALSE,
             size = 6,
             nudge_x = .275,
            colour = '#333333') +
    xlab('Year') +
    ylab('Articles (%) with functional availability') +
    scale_y_continuous(limits = c(0,30), breaks = seq(0,30,10)) +
    scale_fill_manual(values = "#7AD389") +
    labs(fill = NULL) + # hide legend title
    theme_custom() +
    theme(panel.background = element_rect(fill = "ivory"))
```

```{r other_practices_plot, fig.path = "figs/", fig.width = 10/2.54, fig.height = 6/2.54}
plot_other <- plot_data %>%
  filter(practice %in% c("Reporting guidelines", "Conflict of interest", "Funding"), var %in% c("reporting_any", "funding_statement_any", "coi_statement_any")) %>%
  mutate(practice = factor(practice, levels = c("Reporting guidelines", "Conflict of interest", "Funding")),
         practice = fct_recode(practice, "Reporting\nguidelines" = "Reporting guidelines", "Conflict of interest\nstatement" = "Conflict of interest", "Funding\nstatement" = "Funding"),
         type = factor(type)) %>%
  ggplot(aes(x = year, y = percent)) +
  facet_wrap(. ~ practice) +
    geom_pointrange(position = position_dodge(width = .2), shape = 21, size = 1, colour = "#333333",
      aes(
        fill = type,
        ymin = ci_lwr,
        ymax = ci_upr),
      show.legend = FALSE) +
      geom_text(
             aes(label = str_remove(paste0(signif(percent,2),'%'),"^0+")), 
             show.legend = FALSE,
             size = 6,
             nudge_x = .37,
            colour = '#333333') +
    xlab('Year') +
    ylab('Articles (%)') +
    scale_y_continuous(limits = c(0,100), breaks = seq(0,100,25)) +
    scale_fill_manual(values = "#B47AD3") +
    labs(fill = NULL) + # hide legend title
    theme_custom() +
    theme(panel.background = element_rect(fill = "ivory"))
```

This is Figure One of the manuscript.

```{r fig_one, fig.path = "figs/", fig.width = 11.5, fig.height = 14}
plot_grid(plot_core,plot_other, nrow = 2, rel_heights = c(1.5,1))
```
# Supplementary results

## Inter-rater agreement

```{r}
vars <- c("prereg_statement", "measures_statement", "data_statement", "analysis_statement", "reporting_statement", "funding_statement", "coi_statement") # variables we will examine

d_ira <- d %>% # from dataframe d
  filter(article_id %in% c(d_eligible$article_id), # extract only articles that were agreed to be eligible
         coder %in% c("BK", "JB")) %>% # extract only the first and second coder rows
  select(article_id, coder, all_of(vars)) %>%
    mutate(across(all_of(vars), as.factor)) %>%
  pivot_wider(names_from = coder, values_from = all_of(vars),
              names_sep = "_")

# check the factor levels (i.e., response options of BK and JB) match
# identical(levels(d_ira$prereg_statement_BK), levels(d_ira$prereg_statement_JB))
# identical(levels(d_ira$measures_statement_BK), levels(d_ira$measures_statement_JB))
# identical(levels(d_ira$data_statement_BK), levels(d_ira$data_statement_JB))
# identical(levels(d_ira$analysis_statement_BK), levels(d_ira$analysis_statement_JB))
# identical(levels(d_ira$reporting_statement_BK), levels(d_ira$reporting_statement_JB))
# identical(levels(d_ira$funding_statement_BK), levels(d_ira$funding_statement_JB))
# identical(levels(d_ira$coi_statement_BK), levels(d_ira$coi_statement_JB))

d_ira <- d_ira %>%
  mutate(Preregistration = ifelse(prereg_statement_BK == prereg_statement_JB, T, F),
         Measures = ifelse(measures_statement_BK == measures_statement_JB, T, F),
         Data = ifelse(data_statement_BK == data_statement_JB, T, F),
         `Analysis scripts` = ifelse(analysis_statement_BK == analysis_statement_JB, T, F),
         `Reporting guidelines` = ifelse(reporting_statement_BK == reporting_statement_JB, T, F),
         Funding = ifelse(funding_statement_BK == funding_statement_JB, T, F),
         `Conflicts of interest` = ifelse(coi_statement_BK == coi_statement_JB, T, F)) 

# where are the coding differences for the measures variable
d_ira_measures <- d_ira %>% 
  filter(Measures == F) %>% select(article_id, starts_with("measures"), -Measures) %>%
  count(measures_statement_BK, measures_statement_JB) %>%
  arrange(desc(n))

# inter-rater agreement table
d_ira %>%
  summarise(across(c(Preregistration, Measures, Data, `Analysis scripts`, `Reporting guidelines`, Funding, `Conflicts of interest`), ~ mean(.x, na.rm = TRUE))) %>%
  mutate(across(everything(), ~ signif(. * 100, digits = 2))) %>%
  pivot_longer(cols = everything(), names_to = "Practice", values_to = "Inter-rater agreement (%)") %>%
  kable(format = "html")
```

Inter-rater agreement for disclosure statements was high (> 91%) for all variables except for measurement instrument availability (Supplementary Table D1). An examination of the coding differences for measurement instruments showed that for `r d_ira_measures %>% slice(1) %>% pull(n)` articles BK coded that measurement instruments were available and JB coded that they were not. For `r d_ira_measures %>% slice(2) %>% pull(n)` articles, BK used the “unclear” option and JB coded that measurement instruments were not available. Other types of coding differences accounted for fewer than `r d_ira_measures %>% slice(3) %>% pull(n) + 1` articles each. Team discussions highlighted that there were ambiguities in extraction form A (used by BK). TEH resolved these ambiguities and created extraction B (used by JB). Additionally, when coding was compared, TEH reviewed all cases where BK and JB were not in agreement that “NO — there is no measures availability statement”. In the revised coding, there had to be an explicit statement of availability of at least one primary measurement instrument. It was not sufficient for authors to only mention the source of measurement (e.g., by citing a third party). A brief or incomplete description of a measurement instrument also did not suffice — authors had to provide the  measurement instrument, or at least a complete version of the instrument (e.g., all questions from a survey instrument). In some cases, authors shared the questions used for some secondary measures, but did not share the primary measurement instrument. This also did not. If the authors did not clearly identify the primary measures themselves, T.E.H. inferred this by considering measures reported in the abstract to be primary measures). 

## Subgroup analyses based on research type and data type 

```{r}
# Functional preregistration by research type (primary/secondary)
prereg_functional_by_research_type <- d_eligible %>%
  mutate(prereg_access_status = factor(prereg_access_status, levels = c("NO", "YES")), # show zero percentages too
         prereg_access_status = fct_na_value_to_level(prereg_access_status, level = "NO")) %>% # convert NAs to "NO"

  count(research_design, prereg_access_status, .drop = F) %>%
  group_by(research_design) %>%
  mutate(N = sum(n), percent = signif((n/N)*100,2), report = paste0(n,'/',N,' (',percent,'%)')) %>%
  filter(prereg_access_status == "YES") %>%
  mutate(research_design = factor(research_design),
         research_design = fct_recode(research_design, "Primary" = "Primary research study", "Secondary" = "Secondary analysis", "Both research types" = "Primary research study, Secondary analysis")) %>%
  select(research_design, report) %>%
  pivot_wider(names_from = research_design, values_from = report)

# Functional preregistration by data type (quantitative, qualitative)
prereg_functional_by_data_type <- d_eligible %>%
  mutate(prereg_access_status = factor(prereg_access_status, levels = c("NO", "YES")), # show zero percentages too
         prereg_access_status = fct_na_value_to_level(prereg_access_status, level = "NO")) %>% # convert NAs to "NO"
  count(type_of_data, prereg_access_status, .drop = F) %>%
  group_by(type_of_data) %>%
  mutate(N = sum(n), percent = signif((n/N)*100,2), report = paste0(n,'/',N,' (',percent,'%)')) %>%
  filter(prereg_access_status == "YES") %>%
  mutate(type_of_data = factor(type_of_data),
         type_of_data = fct_recode(type_of_data, "Both data types" = "Qualitative, Quantitative")) %>%
  select(type_of_data, report) %>%
  pivot_wider(names_from = type_of_data, values_from = report)

# Combine prereg
prereg_subgroup <- bind_cols(prereg_functional_by_research_type, prereg_functional_by_data_type) %>%
  mutate(`Practice` = "Preregistration")

# Functional measurement sharing by research type (primary/secondary)
measures_functional_by_research_type <- d_eligible %>%
  mutate(measures_access_status = factor(measures_access_status, levels = c("NO", "YES")), # show zero percentages too
         measures_access_status = fct_na_value_to_level(measures_access_status, level = "NO")) %>% # convert NAs to "NO"

  count(research_design, measures_access_status, .drop = F) %>%
  group_by(research_design) %>%
  mutate(N = sum(n), percent = signif((n/N)*100,2), report = paste0(n,'/',N,' (',percent,'%)')) %>%
  filter(measures_access_status == "YES") %>%
  mutate(research_design = factor(research_design),
         research_design = fct_recode(research_design, "Primary" = "Primary research study", "Secondary" = "Secondary analysis", "Both research types" = "Primary research study, Secondary analysis")) %>%
  select(research_design, report) %>%
  pivot_wider(names_from = research_design, values_from = report)

# Functional measures by data type (quantitative, qualitative)
measures_functional_by_data_type <- d_eligible %>%
  mutate(measures_access_status = factor(measures_access_status, levels = c("NO", "YES")), # show zero percentages too
         measures_access_status = fct_na_value_to_level(measures_access_status, level = "NO")) %>% # convert NAs to "NO"
  count(type_of_data, measures_access_status, .drop = F) %>%
  group_by(type_of_data) %>%
  mutate(N = sum(n), percent = signif((n/N)*100,2), report = paste0(n,'/',N,' (',percent,'%)')) %>%
  filter(measures_access_status == "YES") %>%
  mutate(type_of_data = factor(type_of_data),
         type_of_data = fct_recode(type_of_data, "Both data types" = "Qualitative, Quantitative")) %>%
  select(type_of_data, report) %>%
  pivot_wider(names_from = type_of_data, values_from = report)

# Combine measures
measures_subgroup <- bind_cols(measures_functional_by_research_type, measures_functional_by_data_type) %>%
  mutate(`Practice` = "Measurement instruments")

# Functional data sharing by research type (primary/secondary)
data_functional_by_research_type <- d_eligible %>%
  mutate(data_access_status = factor(data_access_status, levels = c("NO", "YES")), # show zero percentages too
         data_access_status = fct_na_value_to_level(data_access_status, level = "NO")) %>% # convert NAs to "NO"

  count(research_design, data_access_status, .drop = F) %>%
  group_by(research_design) %>%
  mutate(N = sum(n), percent = signif((n/N)*100,2), report = paste0(n,'/',N,' (',percent,'%)')) %>%
  filter(data_access_status == "YES") %>%
  mutate(research_design = factor(research_design),
         research_design = fct_recode(research_design, "Primary" = "Primary research study", "Secondary" = "Secondary analysis", "Both research types" = "Primary research study, Secondary analysis")) %>%
  select(research_design, report) %>%
  pivot_wider(names_from = research_design, values_from = report)

# Functional data by data type (quantitative, qualitative)
data_functional_by_data_type <- d_eligible %>%
  mutate(data_access_status = factor(data_access_status, levels = c("NO", "YES")), # show zero percentages too
         data_access_status = fct_na_value_to_level(data_access_status, level = "NO")) %>% # convert NAs to "NO"
  count(type_of_data, data_access_status, .drop = F) %>%
  group_by(type_of_data) %>%
  mutate(N = sum(n), percent = signif((n/N)*100,2), report = paste0(n,'/',N,' (',percent,'%)')) %>%
  filter(data_access_status == "YES") %>%
  mutate(type_of_data = factor(type_of_data),
         type_of_data = fct_recode(type_of_data, "Both data types" = "Qualitative, Quantitative")) %>%
  select(type_of_data, report) %>%
  pivot_wider(names_from = type_of_data, values_from = report)

# Combine data
data_subgroup <- bind_cols(data_functional_by_research_type, data_functional_by_data_type) %>%
  mutate(`Practice` = "Data")

# Functional analysis script sharing by research type (primary/secondary)
analysis_functional_by_research_type <- d_eligible %>%
  mutate(analysis_access_status = factor(analysis_access_status, levels = c("NO", "YES")), # show zero percentages too
         analysis_access_status = fct_na_value_to_level(analysis_access_status, level = "NO")) %>% # convert NAs to "NO"

  count(research_design, analysis_access_status, .drop = F) %>%
  group_by(research_design) %>%
  mutate(N = sum(n), percent = signif((n/N)*100,2), report = paste0(n,'/',N,' (',percent,'%)')) %>%
  filter(analysis_access_status == "YES") %>%
  mutate(research_design = factor(research_design),
         research_design = fct_recode(research_design, "Primary" = "Primary research study", "Secondary" = "Secondary analysis", "Both research types" = "Primary research study, Secondary analysis")) %>%
  select(research_design, report) %>%
  pivot_wider(names_from = research_design, values_from = report)

# Functional analysis by data type (quantitative, qualitative)
analysis_functional_by_data_type <- d_eligible %>%
  mutate(analysis_access_status = factor(analysis_access_status, levels = c("NO", "YES")), # show zero percentages too
         analysis_access_status = fct_na_value_to_level(analysis_access_status, level = "NO")) %>% # convert NAs to "NO"
  count(type_of_data, analysis_access_status, .drop = F) %>%
  group_by(type_of_data) %>%
  mutate(N = sum(n), percent = signif((n/N)*100,2), report = paste0(n,'/',N,' (',percent,'%)')) %>%
  filter(analysis_access_status == "YES") %>%
  mutate(type_of_data = factor(type_of_data),
         type_of_data = fct_recode(type_of_data, "Both data types" = "Qualitative, Quantitative")) %>%
  select(type_of_data, report) %>%
  pivot_wider(names_from = type_of_data, values_from = report)

# Combine analysis
analysis_subgroup <- bind_cols(analysis_functional_by_research_type, analysis_functional_by_data_type) %>%
  mutate(`Practice` = "Analysis script")

# Reporting guideline use by research type (primary/secondary)
reporting_functional_by_research_type <- d_eligible %>%
  mutate(reporting_statement = factor(reporting_statement)) %>% # show zero percentages too
  count(research_design, reporting_statement, .drop = F) %>%
  group_by(research_design) %>%
  mutate(N = sum(n), percent = signif((n/N)*100,2), report = paste0(n,'/',N,' (',percent,'%)')) %>%
  filter(reporting_statement == "YES — the statement discloses use of at least one reporting guideline") %>%
  mutate(research_design = factor(research_design),
         research_design = fct_recode(research_design, "Primary" = "Primary research study", "Secondary" = "Secondary analysis", "Both research types" = "Primary research study, Secondary analysis")) %>%
  select(research_design, report) %>%
  pivot_wider(names_from = research_design, values_from = report)

# Reporting guideline use by data type (quantitative, qualitative)
reporting_functional_by_data_type <- d_eligible %>%
  mutate(reporting_statement = factor(reporting_statement)) %>% # show zero percentages too
  count(type_of_data, reporting_statement, .drop = F) %>%
  group_by(type_of_data) %>%
  mutate(N = sum(n), percent = signif((n/N)*100,2), report = paste0(n,'/',N,' (',percent,'%)')) %>%
  filter(reporting_statement == "YES — the statement discloses use of at least one reporting guideline") %>%
  mutate(type_of_data = factor(type_of_data),
         type_of_data = fct_recode(type_of_data, "Both data types" = "Qualitative, Quantitative")) %>%
  select(type_of_data, report) %>%
  pivot_wider(names_from = type_of_data, values_from = report)

# Combine reporting
reporting_subgroup <- bind_cols(reporting_functional_by_research_type, reporting_functional_by_data_type) %>%
  mutate(`Practice` = "Reporting guidelines")

# Table 
bind_rows(prereg_subgroup, measures_subgroup, data_subgroup, analysis_subgroup, reporting_subgroup) %>%
  relocate(Practice, Primary, Secondary, `Both research types`, Quantitative, Qualitative, `Both data types`) %>%  # put columns in order
  kable(format = "html") %>%
  add_header_above(
    c(
      " " = 1,
      "Research type" = 3,
      "Data type"     = 3
    ),
    bold = TRUE
  ) %>%
  kable_styling(full_width = FALSE)
```
## Access methods for preregistrations, measurement instruments, data, and analysis scripts. Types of reporting guidelines.

Supplementary Table X. Preregistration registries.

```{r}
prereg_access_overall %>% 
  select("Registry" = prereg_access_method, n) %>% 
  arrange(desc(n)) %>%
  kable(format = "html")
```

Supplementary Table X. Measurement instrument sharing methods.

```{r}
measures_access_method_overall  %>% 
  select("Method" = measures_access_method, n) %>% 
  arrange(desc(n)) %>%
  kable(format = "html")
```

Supplementary Table X. Data sharing methods.

```{r}
data_access_method_overall  %>% 
  select("Method" = data_access_method, n) %>% 
  arrange(desc(n)) %>%
  kable(format = "html")
```

Supplementary Table X. Analysis script sharing methods.

```{r}
analysis_access_method_overall  %>% 
  select("Method" = analysis_access_method, n) %>% 
  arrange(desc(n)) %>%
  kable(format = "html")
```

Supplementary Table X. Types of reporting guidelines used.

```{r}
reporting_type_overall %>%
  select("Guideline" = reporting_type, n) %>% 
  arrange(desc(n)) %>%
  kable(format = "html")
```

# Session Info

Information about the software environment used to run the analyses reported in this script.

```{r}
sessionInfo()
```